Titan GPU model

### 2020-06-04 code/TitanGPUmodel.Rmd
testing reproducibility

---
title: "Titan GPU model"
author: "GO"
output:
  html_document:
    css: style.css
    theme: cerulean
---
```{r setup, include=FALSE}
options(repos = c(CRAN = "http://cran.rstudio.com")) # set CRAN mirror
install.packages("remotes")
remotes::install_github("NikNakk/forestmodel") # only package from GitHub
## all other packages will prompt to install from CRAN

>>>>

---
title: "Titan GPU model"
author: "GO"
output:
  html_document:
    css: style.css
    theme: cerulean
---
```{r setup, include=FALSE}
options(repos = c(CRAN = "http://cran.rstudio.com")) # set CRAN mirror
installed = installed.packages()
if(! "remotes" %in% installed) install.packages("remotes")
if(! ("forestmodel" %in% installed && packageVersion("forestmodel") >= "0.6.1"))
  remotes::install_github("NikNakk/forestmodel") # only package from GitHub
## all other packages will prompt to install from CRAN
